Digging Deeper Into the State of the Practice for Domain Specific Research Software

### 2022-02-18 StateOfPractice/Papers/ICCS-2022-SOP_MethodologyPlusExamples/DigDeep.tex
Edits to ICCS paper

Research software is critical for tackling problems in areas as diverse as
manufacturing, financial planning, environmental policy and medical diagnosis
and treatment.  However, developing reliable, reproducible, sustainable and fast
research software to address new problems is challenging because of the
complexity of the physical models and the nuances of floating point and parallel
computation. The importance of research software and the difficulty with its
development have prompted multiple researchers to investigate how developing
this software differs from other classes of software.  Previous studies have
focused on surveying developers \cite{Carveretc}, developer interviews \cite{}
and case studies \cite{Segal}.  A valuable source of information that has
received less attention is the data in the publicly available software
repositories.  We propose a new methodology for digging deeper into how well
projects are applying best practices by using a combination of manual and
automated techniques to extract repository-based information.

The surveys used in previous studies have tended to recruit participants from
all domains of research software, possibly distinguishing them by programming
language (for instance, R developers \cite{Rstudy}), or by the role of the
developers (for instance postdoctoral researchers \cite{Katz}).  For their part,
case studies have focused on a few specific examples at a time, since that is
the nature of case studies.  We propose applying our new methodology between
these two extremes.  Rather than focus on all research software, or just a few
examples, we will focus on one domain of research software at a time. The
practical reason for defining a domain scope is that digging deep into
repository data takes time, making a broad scope infeasible.  We have the
constraint that the work load for applying the methodology to a given domain
needs to be feasible for a team as small as one individual, and for a time that
is short, ideally around a person month per domain.\footnote{A person month is
considered to be $20$ working days ($4$ weeks in a month, with $5$ days of work
per week) at $8$ person hours per day, or $20 \cdot 8 = 160$ person hours.}
Focusing on one domain at a time has more than just practical advantages.  By
restricting ourselves to a single domain we can bring domain knowledge and
domain experts into the mix.  The domain customized insight provided by the
assessment has the potential to help a specific domain as they adopt and develop
new development practices.  Moreover, providing a means to measure different
domains facilitates uncovering domain specific practices, which can later be
compared and contrasted between different domains.

Our methodology is built around 10 research questions for the domain being
assessed.  The questions are used to structure the presentation of the
methodology, so for each research question we point to the corresponding section
of the paper.  Assuming we have identified the domain of interest, the first question is:

\begin{enumerate}
	\item[RQ\refstepcounter{rqnum}\therqnum \label{RQ_WhatProjects}:] What
	software projects exist in the domain, with the constraint that the source
	code must be available for all identified projects?
	(Section~\ref{methodology})
\end{enumerate}

@@

\begin{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_HighestQuality}:] Which
	of the projects identified in \rqref{RQ_WhatProjects} follow current best
	practices, based on evidence found by experimenting with the software and
	searching the artifacts available in each project's repository? (Section~\ref{AHPresults})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareHQ2Popular}:] How
	similar is the list of top projects identified in \rqref{RQ_HighestQuality}
	to the most popular projects, as viewed by the scientific community? (Section~\ref{repmetrics})
\end{enumerate}

@@

\begin{enumerate}
  \item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareArtifacts}:] How
	do domain projects compare to research software in general with respect to the
	artifacts present in their repositories? (Section~\ref{Sec_CompareArtifacts})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareToolsProjMngmnt}:]
	How do domain projects compare to research software in general with respect to
	the use of tools (Section~\ref{Sec_CompareTools}) for:
	\begin{enumerate} 
		\item [\rqref{RQ_CompareToolsProjMngmnt}.a] development; and,
		\item [\rqref{RQ_CompareToolsProjMngmnt}.b] project management?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareMethodologies}:]
	How do domain projects compare to research software in general with respect to
	principles, processes and methodologies used? (Section~\ref{Sec_CompareMethodologies})
\end{enumerate}

Only so much information can be gleaned by digging into software repositories.
To gain additional insight, we need to interview developers.  We need to learn
their concerns and how they deal with these concerns; we need to learn their
pain points.  We wish to know what practices are used by the top domain
projects, so that others can potentially emulate these practices. We also wish
to identify new practices by borrowing successful ideas from other domains. The
above points are covered by the questions outlined below:

@@

Our methodology answers the research question through inspecting repositories,
using the Analytic Hierarch Process (AHP) for ranking software, interviewing
developers and interacting with at least one domain expert.  We leave the
measurement of the performance, for instance using benchmarks, to other projects
\cite{kaagstrom1998gemm}. The current methodology updates the approach used in
prior assessments of domains like Geographic Information Systems
\cite{SmithEtAl2018_arXivGIS}, Mesh Generators \cite{SmithEtAl2016}, Seismology
software \cite{SmithEtAl2018}, and statistical software for psychology
\cite{SmithEtAl2018_StatSoft}.  Initial tests of the new methodology have been
done for medical image analysis software \cite{Dong2021} and for Lattice
Boltzmann Method (LBM) software \cite{Michalski2021}.  The LBM example will be
used throughout this paper to illustrate the steps in the methodology.  The
paper ends with a summary of potential threats to validity
(Section~\ref{threats}) and our final conclusions and recommendations
(Section~\ref{conclusion}).

\section{Methodology} \label{StepsAQDS}

@@

\begin{enumerate}
  \item Identify the domain of interest. (Section~\ref{SecIdentifyDomain})
	\item List candidate software packages for the domain.
	(Section~\ref{identifysoftware})
	\item Filter the software package list. (Section~\ref{filtersoftware})
	\item Gather the source code and documentation for each software package.
	\item Collect quantitative measures from the project repositories.
	(Section~\ref{empiricalmeasures})
	\item Measure using the measurement template.  The full measurement template
	can be found in \cite{SmithEtAl2021}. (Section~\ref{empiricalmeasures})
	\item Interview the developers. (Section~\ref{SecSurvey})
	\item Use AHP to rank the software packages. (Section~\ref{AHP})
	\item Analyze the results and answer the research questions. (Section~\ref{})
\end{enumerate}

Table~\ref{TabPersonHours} estimates the time required (in person hours) to
complete a state of the practice assessment for a single domain.  The table
assumes that the domain has already been decided and the Domain Expert has been
recruited.  The time spent by the Domain Expert is not included in the numbers
shown in the table, since the amount of time that the domain expert will work
independently of the rest of the assessment team will be small.  Moreover, this
amount of time will vary greatly depending on the preferred work habits of the
Domain Expert.  The table follows the steps outlined above. It is assumed that
the template spreadsheets linked in this document, and the developed AHP tool,
will be employed, rather than developing new tools.  The person hours given are
a rough estimate, based on our experience completing assessments for medical
image analysis software \cite{Dong2021} and for Lattice Boltzmann Method (LBM)
software \cite{Michalski2021}.  The estimate assumes 30 software packages will
be measured; the numbers will need to be adjusted if the total packages changes.
The total number of person hours is \total{totHours} hours.  This is close to
our goal of 1 month of person hours (160 hours).

\begin{table}[h]
  \caption{Estimated Person Hours for Assessing the State of Practice for Domain
  X} \label{TabPersonHours}
  \centering
  \begin{tabular}{p{12.5cm} l}
    \toprule
    \textbf{Task} & \textbf{Hours} \\
    \midrule

    Initial 1 hour meeting with the Domain Expert plus meeting prep & 5
    \addtocounter{totHours}{5} \\

    Identify broad list of candidate software
    (Section~\ref{SecIdentifyCandSoft}) & 12 \addtocounter{totHours}{12} \\

    Filter software list (Section~\ref{SecInitialFilter}) (10 minutes per
    package) & 5 \addtocounter{totHours}{5} \\

	Review software list with Domain Expert (Section~\ref{SecDomainExpert}) & 2
	\addtocounter{totHours}{2} \\

    Domain analysis (with help of Domain Expert)
    (Section~\ref{SecDomainAnalysis}) & 20 \addtocounter{totHours}{20} \\

	Vet domain analysis with Domain Expert (Section~\ref{SecDomainExpert}) & 3
	\addtocounter{totHours}{3} \\

	Gather source code and documentation for each package (10 minutes per
	package)) & 5 \addtocounter{totHours}{5} \\

    Collect repository based data (Section~\ref{SecEmpiricalMeasures}) (10
    minutes per package) & 5 \addtocounter{totHours}{5} \\

	Measure using measurement template (Section~\ref{SecMeasureTemplate}) (2.5
    hours per repo) & 75 \addtocounter{totHours}{75} \\

    Solicit developers for interviews & 2 \addtocounter{totHours}{2} \\

    Conduct interviews (1.5 hour interviews with 10 developers (30\% recruitment
    rate)) & 15 \addtocounter{totHours}{15} \\

    AHP ranking & 2 \addtocounter{totHours}{2} \\

	Work with Domain Expert to vet AHP ranking & 2 \addtocounter{totHours}{2} \\

    Analyze data and answer research questions & 20 \addtocounter{totHours}{20}\\

    \midrule
    \textbf{Total} & \textbf{\thetotHours} \\
    \bottomrule
  \end{tabular}

\end{table}

@@

For the LBM example the initial list had 46 packages \cite{Michalski2021}.

@@

For the running example of LBM filtering by scope, usage, and age decreased the
initial list of 46 to a list of 24. Many of the removed packages could not be
tested as there was no installation guide, they were incomplete, source code was
not publicly available, a license was needed, or the project was out of scope or
not up to a standard that would support incorporating them into this
study~\cite{Michalski2021}. Of the remaining packages, some were kept on the
list despite being marked as dead due to their prevalence on authoritative lists
on LBM software and due to their surface excellence.

@@

Most of the data to be collected should be straightforward from reviewing the
measurement template.  However, in a few cases extra guidance is necessary
to eliminate ambiguity, as follows:

\begin{enumerate}
\item Publications about the software: A list of publications can be found
  directly on the website of some software packages. For others use Google
  Scholar or a similar index.
\item To answer whether there evidence that performance was considered, search
  the software artifacts for any mention of speed, storage, throughput,
  performance optimization, parallelism, multi-core processing, or similar
  considerations. The search function on GitHub can help.
\item Evidence of a getting started tutorial may be found within another
  artifact, like the user manual.
\item To find evidence of continuous integration, search the software artifacts
  for any mention of continuous integration. The search function on GitHub can
  help.  In some cases, \texttt{yaml} files will provide a hint that continuous
  integration is employed.
\end{enumerate}

Tools were use to find some of the measurements, such as the number of files,
number of lines of code (LOC), percentage of issues that are closed, etc. The
tool \href{https://github.com/tomgi/git_stats}{GitStats} was used to measure
each software package's GitHub repository for the number of binary files, the
number of added and deleted lines, and the number of commits over varying time
intervals. The tool \href{https://github.com/boyter/scc}{Sloc Cloc and Code
(scc)} was used to measure the number of text based files as well as the number
of total, code, comment, and blank lines in each GitHub repository.

As in \cite{SmithEtAl2016}, Virtual machines (VMs) are used to provide an
optimal testing environments for each package. VMs were used because it is
easier to start with a fresh environment without having to worry about existing
libraries and conflicts. Moreover, when the tests are complete the VM can be
deleted, without any impact on the host operating system. The most significant
advantage of using VMs is to level the playing field. Every software install
starts from a clean slate, which removes ``works-on-my-computer'' errors.

@@

For the LBM project, our Domain Expert was Dr.\
Zahra Motamed, Assistant Professor of Mechanical Engineering at McMaster
University, Hamilton, Ontario, Canada.

@@

Since each domain we will study will have a reasonably small scope, we will be
able to view the software as constituting a program family.  The concept of a
program family is defined by \cite{parnas1976design} as ``a set of programs
whose common properties are so extensive that it is advantageous to study the
common properties of the programs before analyzing individual members''.
Studying the common properties within a family of related programs is termed a
domain analysis.  For the current methodology time constraints necessitate a
shallow domain analysis.  A table should be constructed that distinguishes the
programs under study by the variabilities that distinguish them.  In research
software the variabilities are often related to assumptions.  Table~\ref{} shows
the variabilities for the LBM software example.

@@

\section{Comparison Between LBM and Research Software for Artifacts}
\label{Sec_CompareArtifacts}

@@

\begin{table}
\begin{center}
\begin{tabular}{ p{12 cm}}
%\toprule
\textbf{Common}\\
\midrule
Developer List, Issue Tracker, Dependency List, Installation Guide, Theory
Notes, Related Publications, Build Files, README File, License, Tutorial,
Version Control\\
%\midrule
\textbf{Less Common}\\
\midrule
Change Log, Design Doc., Functional Spec., Performance Info., Test Cases, User
Manual\\
%\midrule
\textbf{Rare}\\
\midrule
API Doc., Developer Manual, FAQ, Verification Plan, Video Guide, Requirements
Spec.\\
%\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

Although the LBM community participates in most of the practices we found listed
in the general research software guidelines, some recommended practices were not
observed or rarely observed. For instance API documentation was rarely observed
for LBM software, but it is a frequently recommended (Table~\ref{Tbl_Guidelines}).
In addition to the items in the last column of Table~\ref{artifactspresent}, we
can add the following community recommended items that we rarely, if ever,
observed:

\begin{itemize}
\item A roadmap showing what is planned for the future.
\item A code of conduct to explicitly say how developers should treat one
another.
\item Programming style guidelines so that programming labels and formatting are
consistent \cite{TobiasEtAl2018,ThielEtAl2020,OrvizEtAl2017,Zadka2018,vanGompelEtAl2016,WilsonEtAl2014}.  We saw this information as part of
some developer guides, but only rarely.
\item Checklists can be used in projects to ensure that best practices are
followed by all developers.  Some examples include checklists merging branches
into master \cite{Brown2015}, checklists for saving and sharing changes to the
project \cite{WilsonEtAl2016}, checklists for new and departing team members
\cite{HerouxAndBernholdt2018}, checklists for processes related to commits and
releases \cite{HerouxEtAl2008} and checklists for overall software quality
\cite{ThielEtAl2020,SSI2022}.  For LBM software, ESPResSo has a checklist for
managing releases, but otherwise they are used only rarely for LBM.
\item Uninstall instructions \cite{vanGompelEtAl2016} were not observed for any
of the LBM projects.
\end{itemize}

\section{Comparison of Tool Usage Between LBM and Other Research Software}
\label{Sec_CompareTools}

@@

\begin{table}
\begin{center}
\begin{tabular}{ p{12 cm}}
%\toprule
\textbf{Development Tools}\\
\midrule
Continuous Integration, Code Editors, Development Environments, Runtime
Environments, Compilers, Unit Testing Tools, Correctness Verification Tools\\
%\midrule
\textbf{Dependencies}\\
\midrule
Build Automation Tools, Technical Libraries, Domain Specific Libraries\\
%\midrule
\textbf{Project Management Tools}\\
\midrule
Collaboration Tools, Email, Change Tracking Tools, Version Control Tools, Document Generation Tools\\
%\bottomrule
\end{tabular}
\caption{Observed development tools, dependencies and project management tools} 
\label{tbl_tools}
\end{center}
\end{table}

@@

\section{Comparison of Principles, Process and Methodologies to Research Software in General} \label{Sec_CompareMethodologies}

>>>>

Research software is critical for tackling problems in areas as diverse as
manufacturing, financial planning, environmental policy and medical diagnosis
and treatment.  However, developing reliable, reproducible, sustainable and fast
research software to address new problems is challenging because of the
complexity of the physical models and the nuances of floating point and parallel
computation. The importance of research software and the difficulty with its
development have prompted multiple researchers to investigate how developing
this software differs from other classes of software.  Previous studies have
focused on surveying developers
\cite{HannayEtAl2009,Nguyen-HoanEtAl2010,PintoEtAl2018}, developer interviews
\cite{SandersAndKelly2008} and case studies \cite{CarverEtAl2007,Segal2005}.  A
valuable source of information that has received less attention is the data in
publicly available software repositories.  We propose digging deeper into how
well projects are applying best practices by using a new methodology that
combines manual and automated techniques to extract repository-based
information.

The surveys used in previous studies have tended to recruit participants from
all domains of research software, possibly distinguishing them by programming
language (for instance, R developers \cite{PintoEtAl2018}), or by the role of
the developers (for instance postdoctoral researchers \cite{UditAndKatz2017}).
Case studies, on the other hand, have focused on a few specific examples at a
time, as is the nature of case studies.  For our new methodology, we propose a
scope between these two extremes.  Rather than focus on all research software,
or just a few examples, we will focus on one domain of research software at a
time. The practical reason for defining a domain scope is that digging deep into
repository data takes time, making a broad scope infeasible. We have determined
that a practical constraint for the work load is for a team as small as one
individual doing one person month worth of work per domain.\footnote{A person
month is considered to be $20$ working days ($4$ weeks in a month, with $5$ days
of work per week) at $8$ person hours per day, or $20 \cdot 8 = 160$ person
hours.} Focusing on one domain at a time has more than just practical
advantages.  By restricting ourselves to a single domain we can bring domain
knowledge and domain experts into the mix.  The domain customized insight
provided by the assessment has the potential to help a specific domain as they
adopt and develop new development practices.  Moreover, measuring different
domains facilitates uncovering domain specific practices, which can later be
compared and contrasted.

Our methodology is built around 10 research questions.  Assuming that the domain
has been identified (Section~\ref{SecIdentifyDomain}), the first question is:

\begin{enumerate}
	\item[RQ\refstepcounter{rqnum}\therqnum \label{RQ_WhatProjects}:] What
	software projects exist in the domain, with the constraint that the source
	code must be available for all identified projects?
	(Sections~\ref{identifysoftware},~\ref{filtersoftware})
\end{enumerate}

@@

\begin{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_HighestQuality}:] Which
	of the projects identified in \rqref{RQ_WhatProjects} follow current best
	practices, based on evidence found by experimenting with the software and
	searching the artifacts available in each project's repository? (Sections~\ref{empiricalmeasures},~\ref{AHP})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareHQ2Popular}:] How
	similar is the list of top projects identified in \rqref{RQ_HighestQuality}
	to the most popular projects, as viewed by the scientific community? (Section~\ref{repmetrics})
\end{enumerate}

@@

\begin{enumerate}
  \item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareArtifacts}:] How
	do domain projects compare to research software in general with respect to the
	artifacts present in their repositories? (Section~\ref{Sec_CompareArtifacts})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareToolsProjMngmnt}:]
	How do domain projects compare to research software in general with respect to
	the use of tools (Section~\ref{Sec_CompareTools}) for:
	\begin{enumerate} 
		\item [\rqref{RQ_CompareToolsProjMngmnt}.a] development; and,
		\item [\rqref{RQ_CompareToolsProjMngmnt}.b] project management?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareMethodologies}:]
	How do domain projects compare to research software in general with respect to
	the processes used? (Section~\ref{Sec_CompareMethodologies})
\end{enumerate}

Only so much information can be gleaned by digging into software repositories.
To gain additional insight, we need to interview developers
(Section~\ref{SecSurvey}).  We need to learn their concerns and how they deal
with these concerns; we need to learn their pain points.  We wish to know what
practices are used by the top domain projects, so that others can potentially
emulate these practices. We also wish to identify new practices by borrowing
successful ideas from other domains. The above points are covered by the
questions outlined below:

@@

Our methodology answers the research question through inspecting repositories,
using the Analytic Hierarch Process (AHP) for ranking software, interviewing
developers and interacting with at least one domain expert.  We leave the
measurement of the performance, for instance using benchmarks, to other projects
\cite{KaagstromEtAl1998}. The current methodology updates the approach used in
prior assessments of domains like Geographic Information Systems
\cite{SmithEtAl2018_arXivGIS}, Mesh Generators \cite{SmithEtAl2016}, Seismology
software \cite{SmithEtAl2018}, and statistical software for psychology
\cite{SmithEtAl2018_StatSoft}.  Initial tests of the new methodology have been
done for medical image analysis software \cite{Dong2021} and for Lattice
Boltzmann Method (LBM) software \cite{Michalski2021}.  The LBM example will be
used throughout this paper to illustrate the steps in the methodology.  The
paper ends with a summary of potential threats to validity
(Section~\ref{threats}) and our final conclusions and recommendations
(Section~\ref{SecConcludingRemarks}).

\section{Methodology} \label{methodology}

@@

\begin{enumerate}
  \item Identify the domain of interest. (Section~\ref{SecIdentifyDomain})
	\item List candidate software packages for the domain.
	(Section~\ref{identifysoftware})
	\item Filter the software package list. (Section~\ref{filtersoftware})
	\item Gather the source code and documentation for each software package.
	\item Collect quantitative measures from the project repositories.
	(Section~\ref{empiricalmeasures})
	\item Measure using the measurement template.  The full measurement template
	can be found in \cite{SmithEtAl2021}. (Section~\ref{empiricalmeasures})
	\item Interview the developers. (Section~\ref{SecSurvey})
	\item Use AHP to rank the software packages. (Section~\ref{AHP})
	\item Analyze the results and answer the research questions. (Sections~\ref{repmetrics}---\ref{Sec_Recommendations}) %,~\ref{Sec_CompareArtifacts},~\ref{Sec_CompareTools},~\ref{Sec_CompareMethodologies},~\ref{painpoints},~\ref{Sec_AddressConcerns},
\end{enumerate}

Close to our goal of 160 person hours, we estimate 173 hours to complete the
assessment of a given domain~\cite{SmithEtAl2021}.  This estimate assumes that
the domain has already been decided and the Domain Expert has been recruited.
The estimate assumes that the template spreadsheets and developed AHP
tool~\cite{SmithEtAl2021}, will be employed, rather than developing new tools.
The person hours given are a rough estimate, based on our experience completing
assessments for medical image analysis software \cite{Dong2021} and for Lattice
Boltzmann Method (LBM) software \cite{Michalski2021}.  The estimate assumes 30
software packages will be measured; the numbers will need to be adjusted if the
total packages changes.

@@

@@

For the LBM example the initial list had 46 packages~\cite{Michalski2021}. For
the running example of LBM filtering by scope, usage, and age decreased the
initial list of 46 to a list of 24. Many of the removed packages could not be
tested as there was no installation guide, they were incomplete, source code was
not publicly available, a license was needed, or the project was out of scope or
not up to a standard that would support incorporating them into this
study~\cite{Michalski2021}. Of the remaining packages, some were kept on the
list despite being marked as dead due to their prevalence on authoritative lists
on LBM software and due to their surface excellence.

@@

Tools are used to find some of the measurements, such as the number of files,
number of lines of code (LOC), percentage of issues that are closed, etc. The
tool \href{https://github.com/tomgi/git_stats}{GitStats} was used to measure
each software package's GitHub repository for the number of binary files, the
number of added and deleted lines, and the number of commits over varying time
intervals. The tool \href{https://github.com/boyter/scc}{Sloc Cloc and Code
(scc)} was used to measure the number of text based files as well as the number
of total, code, comment, and blank lines in each GitHub repository.

As in \cite{SmithEtAl2016}, Virtual machines (VMs) are used to provide an
optimal testing environments for each package. VMs are used because it is
easier to start with a fresh environment without having to worry about existing
libraries and conflicts. Moreover, when the tests are complete the VM can be
deleted, without any impact on the host operating system. The most significant
advantage of using VMs is to level the playing field. Every software install
starts from a clean slate, which removes ``works-on-my-computer'' errors.

@@

@@

Since each domain we will study will have a reasonably small scope, we will be
able to view the software as constituting a program family.  The concept of a
program family is defined by~\cite{parnas1976design} as ``a set of programs
whose common properties are so extensive that it is advantageous to study the
common properties of the programs before analyzing individual members''.
Studying the common properties within a family of related programs is termed a
domain analysis.  For the current methodology time constraints necessitate a
shallow domain analysis.  A table should be constructed that distinguishes the
programs under study by the variabilities that distinguish them.  In research
software the variabilities are often related to assumptions.  Table~\ref{} shows
the variabilities for the LBM software example.

@@

\section{Comparison of Artifacts to Other Research Software}
\label{Sec_CompareArtifacts}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ p{12 cm}}
%\toprule
\textbf{Common}\\
\midrule
Developer List, Issue Tracker, Dependency List, Installation Guide, Theory
Notes, Related Publications, Build Files, README File, License, Tutorial,
Version Control\\
%\midrule
\textbf{Less Common}\\
\midrule
Change Log, Design Doc., Functional Spec., Performance Info., Test Cases, User
Manual\\
%\midrule
\textbf{Rare}\\
\midrule
API Doc., Developer Manual, FAQ, Verification Plan, Video Guide, Requirements
Spec.\\
%\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

Although the LBM community participates in most of the practices we found listed
in the general research software guidelines, some recommended practices were not
observed or rarely observed. The following community recommended items were
rarely, if ever, observed: API documentation, a roadmap, a code of conduct,
programming style guide, uninstall instructions.

\section{Comparison of Tools to Other Research Software}
\label{Sec_CompareTools}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ p{12 cm}}
%\toprule
\textbf{Development Tools}\\
\midrule
Continuous Integration, Code Editors, Development Environments, Runtime
Environments, Compilers, Unit Testing Tools, Correctness Verification Tools\\
%\midrule
\textbf{Dependencies}\\
\midrule
Build Automation Tools, Technical Libraries, Domain Specific Libraries\\
%\midrule
\textbf{Project Management Tools}\\
\midrule
Collaboration Tools, Email, Change Tracking Tools, Version Control Tools, Document Generation Tools\\
%\bottomrule
\end{tabular}
\caption{Observed development tools, dependencies and project management tools} 
\label{tbl_tools}
\end{center}
\end{table}

@@

\section{Comparison of Processes to Other Research Software} \label{Sec_CompareMethodologies}
